Technology games. As Coeckelbergh pointed out, it is the task of
technology games to reveal the hidden depth grammars of technology. The
scope of properly addressing OKM in terms of technology games and its
grammar is far too extensive for this brief section. A social,
historical, and cultural account of academic search engines might be an
interesting task for the future, but for now I hope to show an way of
thinking about OKM with technology games in mind. Table 1 gave a (very)
elementary and subjective overview of a few communication channels and
their characteristics. To the avid user of the internet it comes as no
surprise that the directionality of communication has changed in the
recent decades with the conception of the internet and the recent rise
of the web 2.0\footnote{} Nevertheless,
scholarly publishing has not adopted web 2.0 technologies thoroughly,
yet. Open Science, open access and similar initiatives are advocating
for a change in scholarship, but the discovery process of knowledge is
still dominated by the traditional approaches that were conceived in the
context of archiving and library sciences. The idea of browsing lists of
individual entries based on keywords was useful when the review of texts
on a bigger scale was simply not feasible, but modern technology and the
increased acceptance of Open Access are game changers. OKM and its
design is strongly grounded in this cultural and historical changes of
scholarship. Thus, the study of these changes is not only relevant to
the historians and sociologists of science, but being aware of the
existing grammars of technology could be essential to a technology of
scholarly communication in the 21st century.